Incentivizing Exploration with Unbiased Histories

### 2019-02-01 COLT 2019 Submission/intro.tex
\cite -> \citep in some places.

This situation can be circumvented by a centralized algorithm that induces agents to take explorative actions, an idea called {\em incentivizing exploration}.  Such algorithms are often encountered in the form of recommendations and are quite common in practice.  Many online websites, like Amazon, Reddit, Yelp, and Tripadvisor, among many others, use recommendation policies of some sort to help users navigate their offerings.
%
One way recommendation policies induce exploration is to introduce payments, \eg~\cite{Frazier-ec14,KKMPRVW17,Kempe-colt18}. For example, the recommendation system of an online retailer might offer coupons to agents for trying certain products.  When payments are financially or technologically infeasible, another alternative is to rely on information asymmetry, \eg~\cite{Kremer-JPE14,Che-13,ICexploration-ec15,Bimpikis-exploration-ms17}.
Here the idea is that the centralized algorithm, often called a {\em disclosure policy}, can choose to selectively release information about the past actions and rewards to the agents in the form of a {\em message}.  For example, the recommendation system of an online retailer might disclose past reviews or product rankings to the agents.  Importantly, agents can not directly observe the past, but only learn about it through this message.  The agent then chooses an action, using the content of the message as input.

>>>>

This situation can be circumvented by a centralized algorithm that induces agents to take explorative actions, an idea called {\em incentivizing exploration}.  Such algorithms are often encountered in the form of recommendations and are quite common in practice.  Many online websites, like Amazon, Reddit, Yelp, and Tripadvisor, among many others, use recommendation policies of some sort to help users navigate their offerings.
%
One way recommendation policies induce exploration is to introduce payments, \eg~\citep{Frazier-ec14,KKMPRVW17,Kempe-colt18}. For example, the recommendation system of an online retailer might offer coupons to agents for trying certain products.  When payments are financially or technologically infeasible, another alternative is to rely on information asymmetry, \eg~\citep{Kremer-JPE14,Che-13,ICexploration-ec15,Bimpikis-exploration-ms17}.
Here the idea is that the centralized algorithm, often called a {\em disclosure policy}, can choose to selectively release information about the past actions and rewards to the agents in the form of a {\em message}.  For example, the recommendation system of an online retailer might disclose past reviews or product rankings to the agents.  Importantly, agents can not directly observe the past, but only learn about it through this message.  The agent then chooses an action, using the content of the message as input.
